### 2020-07-15 code/figure2.Rmd
merge master to Peter branch. update figure codes. delete old figure code in text folder

```{r figure-2-plot, fig.width=72, fig.height=48, fig.cap="Figure 2: Pan-cancer enrichment of pathway disruptions. Waterfall plot; columns represent tumors. Each row represents a pathway. The pathways are ranked such that the pathway with the most disruptions across all 7,607 tumors is the first row _etc._ and tumors are ordered to prioritize the top pathway disruptions successively. All 377 pathways are shown. Red signifies pathway disrupted pathways, grey signifies not disrupted."}

## top100 pathways pancancer oncoprint
load("../data/onco_ggplot.Rda") ## load data
onco_color <- c("0" = "grey", "1" = "firebrick3") ## color scheme for oncoprint

>>>>

```{r figure-2-plot, fig.width=72, fig.height=48, fig.cap="Figure 2: Pan-cancer enrichment of pathway disruptions. Waterfall plot; columns represent tumors. Each row represents a pathway. The pathways are ranked such that the pathway with the most disruptions across all 7,607 tumors is the first row _etc._ and tumors are ordered to prioritize the top pathway disruptions successively. All 377 pathways are shown. Red signifies pathway disrupted pathways, grey signifies not disrupted."}
## top100 pathways pancancer oncoprint
load("../data/onco_ggplot.Rda") ## load data
onco_color <- c("0" = "grey", "1" = "firebrick3") ## color scheme for oncoprint
